---
title: "Lab 01 - Hello R"
author: "Lucy D'Agostino McGowan"
date: "2022-01-10"
format: 
  html:
    self-contained: true
editor: visual
---

### Load packages

```{r load-packages, message = FALSE, warning = FALSE}
library(tidyverse) 
library(ISLR)
```


### Exercise 1

(Type your answer to Exercise 1 here. This exercise does not require any R code.)

## Exercise 2

(The answers for this Exercise are given for you below. Delete this explanation line)

```{r add-variable}
Smarket <- Smarket |>
  group_by(Year) |>
  mutate(day = 1:n())
```

### Exercise 3

(The answers for this Exercise are given for you below. But you should clean up some of the narrative so that it only includes what you want to turn in.)

First let's filter the data set to only include rows `Year` is 2001. Then create a visualization of the Volume by day for the year 2001.

```{r plot-2001}
smarket_2001 <- Smarket |>
  filter(Year == 2001)

ggplot(data = smarket_2001, mapping = aes(x = day, y = Volume)) +
  geom_point() + 
  labs(title = "Volume for 2001")
```

And finally calculate the average Volume in 2001.

```{r avg-2001}
smarket_2001 |>
  summarize(avg_volume = mean(Volume))
```

### Exercise 4

(Add code and narrative as needed. Note that the R chunks are labeled with `plot-2002` and `avg-2002` to provide spaces to place the code for plotting and calculating the average volume. To finish, clean up the narrative by removing these instructions.)

Blah blah blah...

```{r plot-2002}
```

I'm some text, you should replace me with more meaningful text...

```{r avg-2002}
```

### Exercise 5

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r}
```

```{r}
```

### Exercise 6

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)
